\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-07-11 scratch/notes_john/JSS-article/JSS-article-4.Rmd
tweak Figs 6 & 7 in JSS-article-4

The \code{Auto} data appeared in a preliminary example in Section \ref{preliminary-example-polynomial-regression}, where we employed CV to inform the selection of the degree of a polynomial regression of \code{mpg} on \code{horsepower}. Here, we consider more generally the problem of predicting \code{mpg} from the other variables in the \code{Auto} data. We begin with a bit of data management, and then examine the pairwise relationships among the numeric variables in the data set (Figure \ref{fig:Auto-explore} (a), produced by the \code{scatterplotMatrix()} function in the \pkg{car} package); in each panel, the solid line shows the linear least-squares fit and the broken line is for a nonparametric regression.:
```{r Auto-explore, fig.show="hold", echo=FALSE}
#| out.width = "65%",
#| fig.align = 'center',
#| fig.height = 4.5,
#| fig.ncol = 1,
#| fig.cap = "(a) Scatterplot matrix for the numeric variables in the \\code{Auto} data.  (b) Component + residual plots for the working model fit to the \\code{Auto} data.",
#| fig.subcap=rep("", 2)
Auto$cylinders <- factor(Auto$cylinders,
                         labels = c("3-4", "3-4", "5-6", "5-6", "8"))
Auto$year <- as.factor(Auto$year)
Auto$origin <- factor(Auto$origin,
                      labels = c("America", "Europe", "Japan"))
rownames(Auto) <- make.names(Auto$name, unique = TRUE)
Auto$name <- NULL

@@

```{r Auto-explore-show, eval=FALSE}
Auto$cylinders <- factor(Auto$cylinders,
                         labels = c("3-4", "3-4", "5-6", "5-6", "8"))
Auto$year <- as.factor(Auto$year)
Auto$origin <- factor(Auto$origin,
                      labels = c("America", "Europe", "Japan"))
rownames(Auto) <- make.names(Auto$name, unique = TRUE)
Auto$name <- NULL

>>>>

The \code{Auto} data appeared in a preliminary example in Section \ref{preliminary-example-polynomial-regression}, where we employed CV to inform the selection of the degree of a polynomial regression of \code{mpg} on \code{horsepower}. Here, we consider more generally the problem of predicting \code{mpg} from the other variables in the \code{Auto} data. We begin with a bit of data management, and then examine the pairwise relationships among the numeric variables in the data set (Figure \ref{fig:Auto-explore} (a), produced by the \code{scatterplotMatrix()} function in the \pkg{car} package); in each panel, the solid line shows the linear least-squares fit and the broken line is for a nonparametric regression.:
```{r Auto-explore, fig.show="hold", echo=FALSE}
#| out.width = "65%",
#| fig.align = 'center',
#| fig.height = 4.5,
#| fig.ncol = 1,
#| fig.cap = "(a) Scatterplot matrix for the numeric variables in the \\code{Auto} data.  (b) Component + residual plots for the working model fit to the \\code{Auto} data.",
#| fig.subcap=rep("", 2)
Auto$cylinders <- factor(Auto$cylinders,
                         labels = c("3-4", "3-4", "5-6", "5-6", "8"))
Auto$year <- as.factor(Auto$year)
Auto$origin <- factor(Auto$origin,
                      labels = c("AMER", "EUR", "JAP"))
rownames(Auto) <- make.names(Auto$name, unique = TRUE)
Auto$name <- NULL

@@

```{r Auto-explore-show, eval=FALSE}
Auto$cylinders <- factor(Auto$cylinders,
                         labels = c("3-4", "3-4", "5-6", "5-6", "8"))
Auto$year <- as.factor(Auto$year)
Auto$origin <- factor(Auto$origin,
                      labels = c("AMER", "EUR", "JAP"))
rownames(Auto) <- make.names(Auto$name, unique = TRUE)
Auto$name <- NULL
